---
title: "My Assignment"
author: "Khalid Saeed"
date: "8/3/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
## knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This project was created as part of the Developing Data Products course of the Coursera [Data Science Specialisation]

## Map of Oil-Filed for Saudi Aramco

The following map represents passenger traffic on the Paris RATP railway network in 2015. Clicking on a station shows the total number of passengers that entered the station during that year.

```{r prerequisites}
rm(list=ls())
library(leaflet)
library(jsonlite)
library(dplyr)
library(stringr)
```

## Summary of Aramco and some oil fields and chemicals

```{r Dammam, echo = TRUE}
  leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lat= 26.487444,lng= 50.119097, popup="Front Sea Corniche") %>%
  addMarkers(lat= 26.290139,lng= 50.106587, popup="Saudi Aramco HQ (Biggest Oil Company)") %>%
  addMarkers(lat= 26.335803,lng= 50.120909, popup="Ithraa Musem (Oil History Musem)") %>%
  addMarkers(lat= 26.325951,lng= 50.137437, popup="King Fahad of Petroleum and Minerals University") %>%
  addMarkers(lat= 26.697720,lng= 50.095779, popup="Ras Tanura Oilfield (Largest Oil-filed)") %>%
  addMarkers(lat= 27.038072,lng= 49.558269, popup="SABIC (Petrochemical Projects)") #%>%
    
```